Evidence of widespread maintenance of functional composition in vertebrate communities

### 2021-09-16 paper/manuscript.Rmd
add citation

journal: "Ecology Letters"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: #word_document
  rticles::elsevier_article:
  includes:
   in_header: preamble.tex
editor_options: 
  markdown: 
    wrap: sentence
---

>>>>

journal: "Ecology Letters"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: #word_document
  rticles::pnas_article:
  includes:
   in_header: preamble.tex
editor_options: 
  markdown: 
    wrap: sentence
---
